### 2020-08-24 7_conclusion.tex
Tweak text.

\begin{itemize}
\item Evaluations of programming system performance should avoid using
  TPS or weak scaling to characterize overheads, as these metrics do
  not constrain the useful work achieved. Instead a metric with
  constrained efficiency, such as METG(50\%), is needed to ensure that
  measurements are representative and fair.

>>>>

\begin{itemize}
\item Evaluations of programming system performance should avoid using
  TPS, or strong or weak scaling to characterize overheads, as these metrics do
  not constrain the useful work achieved. Instead a metric with
  constrained efficiency, such as METG(50\%), is needed to ensure that
  measurements are representative and fair.
